---
title: "Graphhopper Practice"
author: "Max O'Krepki"
date: "August 17, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("C:\\Users\\Derek\\Documents\\GitHub\\graphhopper\\graphhopper_R_practice")
```

Libraries 
```{r}
library(httr)
library(jsonlite)
library(rbenchmark)
library(dplyr)
```


This all works for Berlin, down below I'll try the Bay Area. 


Making a sample request to the local instance of graphhopper 
```{r}
benchmark({
response <- GET("http://localhost:8989/route?point=52.52583%2C13.388214&point=52.512356%2C13.384695")
results  <- fromJSON(content(response, 'text'))}
replications = 1)
```

Returned distance is in meters and time in ms (1 min = 60,000 ms)
```{r}
results  <- GET("http://localhost:8989/route?point=52.52583%2C13.388214&point=52.512356%2C13.384695") %>% content("text") %>% fromJSON()
paste(round(results$paths$distance/1000,2), "km")
paste(round(results$paths$time/60000, 2), "min")
```

Public transit practice for around Berlin.......appears to work!!!!!!!

```{r}
results  <- GET("http://localhost:8989/route?point=52.52583%2C13.388214&point=52.512356%2C13.384695&pt.earliest_departure_time=2018-08-30T15%3A40%3A00.000Z") %>% content("text") %>% fromJSON()
paste(round(results$paths$distance/1000,2), "km")
paste(round(results$paths$time/60000, 2), "min")
```

Now do a stress test for transit. 
```{r}
benchmark({GET("http://localhost:8989/route?point=52.52583%2C13.388214&point=52.512356%2C13.384695&pt.earliest_departure_time=2018-08-30T15%3A40%3A00.000Z&") %>% content("text") %>% fromJSON()}, replications = 10000);
```

843.68/10000 = 0.084368s/request 
A bit slower than other modes at just under 12 requests per second. 
Still, it's free though so that's hard to complain. 


Practice with bike, and foot. Voila! They both work. Now the momen we've all been waiting for, the California test.....ding ding ding ding ding! It works!
```{r}
results  <- GET("http://localhost:8989/route?point=38.008066%2C-122.115784&point=37.425798%2C-122.169685&vehicle=car") %>% content("text") %>% fromJSON()
paste(round(results$paths$distance/1000,2), "km")
paste(round(results$paths$time/60000, 2), "min")
```

```{r}
benchmark({GET("http://localhost:8989/route?point=52.52583%2C13.388214&point=52.512356%2C13.384695") %>% content("text") %>% fromJSON()}, replications = 10000)
```

66.78/10000 = 0.006678s/request
Pretty fast about 149 requests per second

Total requests
2700*197*4
Estimated total time in hours ~4
2700*197*4*0.006678/3600


Do a quick test with the california file. Note that is uses a different storage option. 
```{r}
benchmark({GET("http://localhost:8989/route?point=38.008066%2C-122.115784&point=37.425798%2C-122.169685&vehicle=car") %>% content("text") %>% fromJSON()}, replications = 10000)
```
135.26/10000 = 0.013526s/request
About 74 requests per second. Slower but still not to bad I think. 
